Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Byzantium version \YellowPaperVersionNumber}}

### 2018-04-09 Paper.tex
Seed hash is just zero for epoch 0
Fixes https://github.com/ethereum/yellowpaper/issues/312
Clarify CODESIZE behavior during contract initialization
Fixes https://github.com/ethereum/yellowpaper/issues/391

\subsection{Subtleties}
Note that while the initialisation code is executing, the newly created address exists but with no intrinsic body code. Thus any message call received by it during this time causes no code to be executed. If the initialisation execution ends with a {\small SELFDESTRUCT} instruction, the matter is moot since the account will be deleted before the transaction is completed. For a normal {\small STOP} code, or if the code returned is otherwise empty, then the state is left with a zombie account, and any remaining balance will be locked into the account forever.

@@

\subsection{Instruction Set}

>>>>

\subsection{Subtleties}
Note that while the initialisation code is executing, the newly created address exists but with no intrinsic body code\footnote{During initialization code execution, \texttt{EXTCODESIZE} on the address should return zero, which is the length of the code of the account while \texttt{CODESIZE} should return the length of the initialization code (as defined in \ref{subsec:instruction-set}).}. Thus any message call received by it during this time causes no code to be executed. If the initialisation execution ends with a {\small SELFDESTRUCT} instruction, the matter is moot since the account will be deleted before the transaction is completed. For a normal {\small STOP} code, or if the code returned is otherwise empty, then the state is left with a zombie account, and any remaining balance will be locked into the account forever.

@@

\subsection{Instruction Set}
\label{subsec:instruction-set}
